### 2025-09-01 machine-learning.qmd
20250901 - tidymodeling

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.
For each of the models, we fit and evaluate the models using the `tidymodels` ecosystem of packages [@R-tidymodels; @Kuhn2020_packages].
we specify our model formula using the `recipes::recipe()` function of the `recipes` package [@R-recipes].
We define the model using the `parsnip::linear_reg()`, `parsnip::set_engine()`, and `parsnip::set_mode()` functions of the `parsnip` package [@R-parsnip].
We specify the workflow using the `workflows::workflow()`, `workflows::add_recipe()`, and `workflows::add_model()` functions of the `workflows` package [@R-workflows].
We fit the cross-validation model using the `tune::fit_resamples()` function of the `tune` package [@R-tune].
We specify the accuracy metrics to evaluate using the `yardstick::metric_set()` function of the `yardstick` package [@R-yardstick].
We fit the final model using the `workflows::fit()` function of the `workflows` package [@R-workflows].
We evaluate the accuracy of the model's predictions on the test data using the `petersenlab::accuracyOverall()` of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab].

>>>>

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.
For each of the models, we fit and evaluate the models using the `tidymodels` ecosystem of packages [@R-tidymodels; @Kuhn2020_packages].
Modeling using `tidymodels` is described in @Kuhn2023: <https://www.tmwr.org>.
We specify our model formula using the `recipes::recipe()` function of the [`recipes`](recipes::recipes) package [@R-recipes].
We define the model using the `parsnip::linear_reg()`, `parsnip::set_engine()`, and `parsnip::set_mode()` functions of the `parsnip` package [@R-parsnip].
We specify the workflow using the `workflows::workflow()`, `workflows::add_recipe()`, and `workflows::add_model()` functions of the `workflows` package [@R-workflows].
We fit the cross-validation model using the `tune::fit_resamples()` function of the `tune` package [@R-tune].
We specify the accuracy metrics to evaluate using the `yardstick::metric_set()` function of the `yardstick` package [@R-yardstick].
We fit the final model using the `workflows::fit()` function of the `workflows` package [@R-workflows].
We evaluate the accuracy of the model's predictions on the test data using the `petersenlab::accuracyOverall()` of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab].
